Boundary Labeling for annotated documents

### 2018-02-21 LaTeX/Paper.tex
Paper: Moved and re-wrote Definition of SP-Paths, cleared up unused comments and files. Program: no changes.

Since we only allowed the Usage of O- and P-Segments in leaders, the only way for a leader to cross through a line of text is with a P-Segment through whitespace, whereas O-Segments are only usable between lines. Therefore, we can create a routing graph $G=\langle V,E\rangle$ whose Edges $E$ reflect the legal paths a leader can take within $T$.
For each line $l_i \in L$ and each whitespace character $h \in l_i$, one vertex is placed in $s_i$ and $s_{i+1}$ each, located above or below the whitespace character, and with a maximum distance from each of its neighbouring lines. The start and end of each line are also assigned a pair of vertices each. Sites will be represented by the insertion of additional vertices in $S_i$ on a similar height as those next to whitespace of the same line and located directly above the center point of its words $w_j$ bounding rectangle $R(w_j)$. The edges between the vertices are all perfectly horizontal or vertical, and do neither intersect with any bounding rectangle, nor any vertices other than their starting and ending vertex. The resulting graph looks similar to Fig.~\ref{fig:rgraph}.

Each edge has a capacity of 1, meaning that no more than one leader is allowed to pass through it. Leaders also aren't allowed to cross one another, as it is hard to discern between intersections and two leaders curving away from each other. They are also monotonically increasing, and go as far up as possible, limited only by the previous label's placement. %This is realized by forcing leaders to incorporate as many P-Segments as early as possible while still following all previous restrictions, and forbidding leaders from entering the space to the top left of already successfully routed leader's sites.
%In our algorithm, the focus was put on keeping the text as readable as possible. This means that leaders aren't allowed to pass through words - they can only use the space between words and in between lines.
%Additionally, we wanted to maximize the usage of the label area's space, even if we have to move labels further from their sites than needed. 
%Finally, we wanted to keep the leader's length low for any given combination of labels and site placements, so every segment of a leader has to decrease the remaining distance between the site and its label's port.

%\begin{figure}
% \captionsetup{justification=centering, margin=0.75cm}
% \centering
%  \makebox[\textwidth][c]{\includegraphics[scale=0.9]{FromTextToGraph.png}}
%  \caption{Visualization of the space reserved for the text, and the resulting graph.}
% \label{fig:ttg}
%\end{figure}

%These properties were modelled by creating a rectangle around each word that no leaders may pass through. If this is done for all words in a paragraph, the remaining available space for routing resembles a grid, like in Fig.\ref{fig:ttg}a.

%Since the layout encourages the usage of P- and O-segments, we decided to represent the possible routes by creating a graph which has its vertices located whenever multiple directions are available - in between lines, above or below whitespace characters. The graph's edges represent the different possible segments of a leader and connect each vertex with the closest vertices directly above, below or to the sides, given that no text is blocking the connection. The resulting graph looks similar to the one in Fig.~\ref{fig:ttg}b.

%For ease of visualisation, we limited the number of leaders per edge to one, and forbid the leaders to cross one another, as this could be mistaken for two leaders touching each other at the corners. We also decided to place the annotations in the order in which they appear in the text, and always place their port above the leader's source, which means that crossings are inevitable if a leader is located above and to the left of an earlier leader. To ensure this never happens, leaders aren't allowed to enter the top left quadrant of a source vertex, unless no routing could be found for that vertex, which means there won't be any leaders to collide with. Additionally, to keep the leader's length minimal, each leader is only allowed to move towards the source, which places a hard limit on how far up a leader is allowed to go, and restricts the possible choices at each node to edges that allow the leader to move in that direction.
%To maximize the space available to subsequent annotations, each label is placed as far up as possible. This also means that if there's no placement available that is above its leader's source, the annotation cannot be placed, as we previously restricted the leader's movement.

%This was implemented by enclosing each word in a bounding rectangle that leaders aren't allowed to pass through.
%The leaders should also be kept as short as possible, so we restricted them to always be moving toward the label, even if the direct route is unavailable.%Wie drücke ich das als Formel aus?
%We also wanted to use the space available in the labeling area as efficiently as possible, so labels are placed as far up as possible in order to maximize the space available to future labels at the cost of increased leader length.

@@

The routing algorithm works through the annotations $a \in A$ in the order they appear in the text, placing each as far up as possible, skipping any annotation that cannot be placed above its leader's source or is impossible to route. It will use fixed ports located in the top left corner of each label. 
The routing area will be used to bridge the gap between the highest currently reachable point within the routing graph and the highest possible label placement by connecting the two via an OPO-leader. We will call the combination of this connecting leader and the path generated within the routing graph a \emph{Source-Port-Path} or \emph{SP-path}.%Kann man das so sagen?

>>>>

Since we only allowed the Usage of O- and P-Segments in leaders, the only way for a leader to cross through a line of text is with a P-Segment through whitespace, whereas O-Segments are only usable between lines. Therefore, we can create a routing graph $G=\langle V,E\rangle$ whose Edges $E$ reflect the legal paths a leader can take within $T$.
For each line $l_i \in L$ and each whitespace character $h \in l_i$, one vertex is placed in $s_i$ and $s_{i+1}$ each, located above or below the whitespace character, and with a maximum distance from each of its neighbouring lines. The start and end of each line are also assigned a pair of vertices each. Sites will be represented by the insertion of additional vertices in $S_i$ on a similar height as those next to whitespace of the same line and located directly above the center point of its words $w_j$ bounding rectangle $R(w_j)$. The edges between the vertices are all perfectly horizontal or vertical, and do neither intersect with any bounding rectangle, nor any vertices other than their starting and ending vertex. The resulting graph looks similar to Fig.~\ref{fig:rgraph}.
\change{We wil call the vertices closest to the text area's border to the routing area \emph{Border Vertices} $B \subset V$. They serve as a goal for the depth-first search, and are located at the end of each line in our implementation.}

Each edge has a capacity of 1, meaning that no more than one leader is allowed to pass through it. Leaders also aren't allowed to cross one another, as it is hard to discern between intersections and two leaders curving away from each other. Furthermore, they are monotonically increasing, and go as far up as possible, limited only by the previous label's placement.

\change{The Routing Area will be used to connect each site's path with its source, using OPO-Leaders. Combined with the path $P=\{s, v_1, v_2, ..., v_b\}; P \subset V$ leading from the source $s \in S$ to the graph's border $(v_b \in B)$ it creates an unbroken connection between a source and its port, which shall be called a \emph{Source-Port-Path}, or \emph{SP-Path}.}
%For ease of visualisation, we limited the number of leaders per edge to one, and forbid the leaders to cross one another, as this could be mistaken for two leaders touching each other at the corners. We also decided to place the annotations in the order in which they appear in the text, and always place their port above the leader's source, which means that crossings are inevitable if a leader is located above and to the left of an earlier leader. To ensure this never happens, leaders aren't allowed to enter the top left quadrant of a source vertex, unless no routing could be found for that vertex, which means there won't be any leaders to collide with. Additionally, to keep the leader's length minimal, each leader is only allowed to move towards the source, which places a hard limit on how far up a leader is allowed to go, and restricts the possible choices at each node to edges that allow the leader to move in that direction.
%To maximize the space available to subsequent annotations, each label is placed as far up as possible. This also means that if there's no placement available that is above its leader's source, the annotation cannot be placed, as we previously restricted the leader's movement.

@@

The routing algorithm works through the annotations $a \in A$ in the order they appear in the text, placing each as far up as possible, skipping any annotation that cannot be placed above its leader's source or is impossible to route. It will use fixed ports located in the top left corner of each label.
